Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-02-02 response/response.tex

\begin{revcomment}[2.10]
    Section 3\\
    \begin{itemize}
        \item Page 8, line 33 "regular commit" - pick baseline or regular (or non-security) commits and use it always.  
        I don't understand the sentence "The baseline dataset is generated from the security commits dataset."   
        Do you mean you extract these commits from the projects in the security commits dataset?
    \end{itemize}
\end{revcomment}

\Us Yes, for each security commit we collected a random regular change from the same project. We have clarified it 
in the paper.

\begin{revcomment}[2.11]
    Section 3\\
    \begin{itemize}
        \item Section 3.2 is confusing enough that I'm not sure of the analysis - 
        I will need to review the revision that you would submit to gain confidence.  
        Are you saying you want your non-security commits (regular commits) to be about 
        the same size as a given security commit so you are using this criteria to choose 
        your regular commits?  Justify this reasoning and make the methodology clear.  
        I would have expected that you randomly collected 1300 non-security commits to compare 
        with the 1300 security commits. Why constrain to make them be of "similar" size?  
        Why not allow the characteristics of regular versus security commits to be what 
        they are without such curating?
    \end{itemize}
\end{revcomment}

\Us Yes, we are looking for regular changes with the same size as security commits
from the same project. However, 
for some cases, it was difficult to find the exact same size. Thus, we  
searched for an approximation. Every 10 attempts of failling to get a commit with 
the same size, we spanned the range size. We clear the methodology in the paper
in Section 3.2 \textit{(Security Patches vs. Regular Changes)}.

``I would have expected that you randomly collected 1300 non-security commits to compare 
with the 1300 security commits.'': Although we started with 1300 commits, 
$331$ cases were tossed due to BCH limitations. In addition, BCH
takes substantial time to process this amount of cases. 
Since the comparison is between 
the final dataset of $969$ patches and the baselines. We produced d
baselines with the final number of viable results obtained for the security 
dataset.

We 
have collected a baseline of random changes only (no size restrictions) in the past and 
performed the same evaluation. We now present the results for both baselines: \textit{size-baseline}, where we consider
size appproximation; and, \textit{random-baseline}, where we consider all the regular
changes characteristics.

### 2021-02-02 paper/emse20.tex
improving 2.11

@@

As for the security patches, for each regular change or refactoring, we also 
need the commit performing the regular change (\emph{sha-reg}) and version of 
the software before the change (\emph{sha-reg-p}). For each security patch, a 
\emph{diff} with an approximate 
size was fetched to a regular change. Due to the complexity of some patches, it was not possible 
to find patches with the exact number of added and deleted lines. 
Our search uses the security patch \emph{diff} to look for a 
\emph{diff} of the same size. The algorithm integrates the following 
steps:

\begin{enumerate}
\item Calculates the \emph{diff} between the security patch commit 
(\emph{sha}) and its parent (\emph{sha-p}).
\item Selects a random commit from the project (\emph{sha-reg}).
\item Calculates the \emph{diff} between the random commit (\emph{sha-reg}) 
and its parent (\emph{sha-reg-p}).
\item Checks if the size from the regular change has the 
same/approximated size to the security patch.
\end{enumerate}

The pair of the random commit and its parent is accepted if the 
\emph{diff} size fits in the range size. This range widens every 
$10$ attempts to search for a change with the same size. We 
originate the regular changes from the security commits to ensure 
that differences in maintainability are not a consequence of 
characteristics of different projects.

As for the security patches, for each regular change or refactoring, we also 
need the commit performing the regular change (\emph{sha-reg}) and version of 
the software before the change (\emph{sha-reg-p}). For each security patch, 
a random commit is selected from the the project (\emph{sha-reg}).

>>>>

As for the security patches, for each regular change, we also 
need the commit performing the regular change (\emph{sha-reg}) and version of 
the software before the change (\emph{sha-reg-p}). For each security patch, a 
random commit from the same project is selected (\emph{sha-reg}).
\emph{sha-reg-p} is the commit performed previous to the 
regular change, \emph{sha-reg}.

@@

For the size-baseline, we also need to obtain the regular change (\emph{sha-reg})
and the version of the software before the change (\emph{sha-reg-p}). 
First, the \emph{diff}
between the security patch and its parent is calculated.
Then, a random commit/regular change from 
the same project is selected (\emph{sha-reg}). The 
\emph{diff} between \emph{sha-reg} and its parent (\emph{sha-reg-p})
is calculated and compared to the \emph{diff} from the security patch.
Due to the complexity of some patches, it was not possible 
to find patches with the exact number of added and deleted lines. 
Thus, we looked for an approximation.
% The algorithm integrates the following steps:

% \begin{enumerate}
% \item Calculates the \emph{diff} between the security patch commit 
% (\emph{sha}) and its parent (\emph{sha-p}).
% \item Selects a random commit from the project (\emph{sha-reg}).
% \item Calculates the \emph{diff} between the random commit (\emph{sha-reg}) 
% and its parent (\emph{sha-reg-p}).
% \item Checks if the size from the regular change has the 
% same/approximated size to the security patch.
% \end{enumerate}

The pair of the regular change (\emph{sha-reg}) and its parent (\emph{sha-reg-p}) is accepted if the 
\emph{diff} size fits in the range size. This range widens every 
$10$ attempts to search for a change with the same size. We 
originate the regular changes from the security commits to ensure 
that differences in maintainability are not a consequence of 
characteristics of different projects.
